% \section{Introduction}
Hiring new employees is one of the most important and frequent processes in any major business environment. The project at hand facilitates this process. Given a candidate's resume, textual answers to common questions set by interviewer, and a recorded introductory video, "iHire" provides analysis based on that candidate and rank all of the candidates based on their resumes. Using intelligent programs that execute and scale efficiently to make it easier for recruiters (interviewers) to select the best candidate from a large volume of candidates. \newline

A study made by \href{https://www.workstream.us/}{workstream} a hiring agency located in the USA showed that 48\% of new hires fail to suite in within 18 months of being employed, and this shows the complexity and importance of hiring process, as most companies fail to hire the right applicant. \newline

Thus, “iHire” is built to address this problem, a platform designed to help (assist) HRs (interviewers) make good decisions, save their time, and increase productivity; by eliminating the burden of manually evaluating each candidate applying for the job.



\section{Motivation and Justification}
The hiring process requires so much time and effort from HR department and also from the domain specialists; for reviewing applicants’ resumes, interviewing them, and analyzing interviews. On average, each corporate job offer attracts 250 resumes.\\

To chose the right candidate very accurate analysis of the data, categorization, and ranking of each candidate is required. This effort is usually overwhelming for interviewers. Thus, doing this task solely by human interviewers does not guarantee that the chosen applicant was the best fit for the position. In addition human decision may contain some bias. “iHire” goal is to reduce the cost of the hiring process helping interviewers to make the best decisions.

\section{Project Objectives and Problem Definition}
\label{sec:Project Objectives and Problem Definition}

Hiring process is a very complex task. Interviewers have to carefully choose specific resumes among a huge pool of unqualified templates, and try to choose the best fit, and it’s guaranteed that well qualified applicants are missed, so it was never an easy task, "iHire" is built and designed to tackle this problem.\newline

Project's objective is to provide a platform (ie. web application) for interviewers where applicants submit their resumes, a self-recording video introducing themselves, and answering some textual questions provided by the interviewer. By analysing these inputs, we provide a complete personality analysis that helps interviewers making good decisions which will save their time, money and effort. In addition the system gives applicants a fair chance in getting hired. Last but not least the application is designed to be a distributed system that balances the work load among separate machines; to increase the computation power, which makes it executes faster and with high availability.


\section{Project Outcomes}

The project outcome is a platform (ie. web application) that helps interviewers make a good use of their time and money, and reduce the cost of hiring process by taking their collected data, gathered from submitted forms by applicants, and provide a very neat and useful analysis; filtering applicants based on their personalities and ranking them based on how much does their resumes match the job description.

In addition to provide an opportunity for applicants to find valid positions created by interviewers, making it easier for them to reach interviewers through our platform.

\section{Document Organization}

The document consists of six chapters. The first chapter \ref{ch:1} is an introduction to the project that showed project's motivation and objectives, problem definition, and the expected outcome.\newline

The second chapter \ref{ch:2} goes through the market survey; explaining market's needs and targeted customers, also introducing market competitors along with financial analysis with expected revenues.\newline

The third chapter \ref{ch:3} gives a covering literature survey of all concepts and tried methods that we have applied, experimented, and implemented in the project.\newline 

The fourth chapter \ref{ch:4} describes the system design and architecture explaining each module separately and the overall architecture at the end.\newline

The fifth chapter \ref{ch:5} explains how the system was tested, as separable modules, and as a whole working project. Comparing it with the state-of-the-art applications tackling the same problem. \newline

The last chapter \ref{ch:6} gives a conclusion and proposals for future work, the challenges faced and the gained experience.