\section{Market Survey}
Market Survey goes here, I think it should be called Market VISIBILITY study.

In this chapter, you survey the related market to your project. Other similar tools/platforms should be discussed. The drawbacks within them, which justify the need of you project, should be given.

In this space, before the first section, write an introductory paragraph on the project market

\subsection{Targeted Customers}
In this section, mention who are the intended customers of your project and explain how these customers benefit from it


\subsection{Market Survey}
In this section, list the competitive products to your work. Similar commercial tools/platforms should be mentioned and discussed. Write a subsection for everyone of them and explain its pros and cons in that subsection

\subsubsection{Competitive Project 1}
Explain and discuss each competitive project

\subsubsection{Competitive Project 2}
Explain and discuss each competitive project

\subsection{Business Case and Financial Analysis}

In this section you describe the success of establishing a company to sell your product (or service) 

Two Aspects must be addressed
Business Case:   Based on Market survey above you should anticipate how many products you will sell over the next 5 years and how will you set your price to counter the competition.

Financial Analysis: Based on the business case we must anticipate 
The Capex (Capital Expenditure):  These are one-time spending that you pay for development and buying things for the company
The Opex (Operational Expenses): These are recurring payments for salaries and marketing and … etc.
Then you create what we call a cash flow table (on an excel sheet). In this sheet you put down your monthly capex and opex on a set of rows and your reveneus (money you get back from selling product/services) on another set of rows.
The difference between both sums is your profit before tax.
It is likely that this difference is negative at beginning until your sales increase and counter the expenses.
From this cash flow analysis you find the date of the break even point wbich is the date at which all the money you get back equals the money you spent. From that date onward you will be making true profit.
