
\begin{thebibliography}{9}
%% market survey citation
\bibitem{CEIC Survey}
\href{https://www.ceicdata.com/en/egypt/the-egyptian-exchange-number-of-listed-companies/no-of-listed-companies-egx}{Egypt Number of Listed Companies: EGX (2021)}  

\bibitem{Server pricing}
\href{https://gcorelabs.com/pricing/hosting/}{Server hosting pricing}  

\bibitem{ideal}
\href{https://ideal.com}{Ideal website} 

\bibitem{SparkHire}
\href{https://www.sparkhire.com}{SparkHire website} 

\bibitem{SmartRecruiters}
\href{https://www.smartrecruiters.com}{SmartRecruiters website} 

\bibitem{SparkHire Pricing}
\href{https://www.sparkhire.com/pricing}{SparkHire Pricing} 

\bibitem{SmartRecruiters Pricing}
\href{https://www.getapp.com/hr-employee-management-software/a/smartrecruiters/pricing}{SmartRecruiters Pricing}


\bibitem{relu_cite} 
\href{http://www.cs.toronto.edu/~fritz/absps/imagenet.pdf}{Krizhevsky et al. ImageNet Classification with Deep Convolutional
Neural Networks.}.

\bibitem{adam} 
\href{https://arxiv.org/abs/1412.6980}{Diederik P. Kingma, Jimmy Ba. Adam: A Method for Stochastic Optimization}.

\bibitem{rnn_models} 
\href{https://www.infona.pl/resource/bwmeta1.element.baztech-0106e25d-92b6-4c93-8317-367a9f574578/content/partDownload/8f157d44-3fa6-3170-ac91-600887a1f0fb}{Shewalkar, A. Performance evaluation of deep neural networks RNN, LSTM and GRU. Journal of Artificial Intelligence and Soft Computing Research. 2019 Vol. 9, No. 4 235--245}.

\bibitem{rnn_long_term_problem_1} 
\href{https://people.idsia.ch//~juergen/SeppHochreiter1991ThesisAdvisorSchmidhuber.pdf}{Josef Hochreiter. Untersuchungen zu dynamischen neuronalen Netzen}.

\bibitem{Mikolov}
\href{https://papers.nips.cc/paper/2013/file/9aa42b31882ec039965f3c4923ce901b-Paper.pdf}{Mikolov et al. Distributed Representations of Words and Phrases and their Compositionality.}

\bibitem{skip_gram} 
\href{https://arxiv.org/pdf/1301.3781.pdf}{Mikolov et al. Efficient Estimation of Word Representations in Vector Space. [cs.CL] 7 Sep 2013}

\bibitem{bert}
\href{https://arxiv.org/pdf/1810.04805.pdf}{Devlin et al. BERT: Pre-training of Deep Bidirectional Transformers for
Language Understanding. [cs.CL] 24 May 2019}

\bibitem{vgg}
\href{https://arxiv.org/abs/1409.1556}{Karen Simonyan, Andrew Zisserman. Very Deep Convolutional Networks for Large-Scale Image Recognition.}

\bibitem{deepface}
\href{https://ieeexplore.ieee.org/document/9259802}{Serengil et al. LightFace: A Hybrid Deep Face Recognition Framework. 2020 IEEE 10.1109/ASYU50717.2020.9259802}

\bibitem{ariaga}
\href{https://arxiv.org/abs/1710.07557}{Octavio Arriaga et al. Real-time Convolutional Neural Networks for Emotion and Gender Classification. arXiv:1710.07557 [cs.CV]}

\bibitem{who am i}
\href{https://ieeexplore.ieee.org/document/8422105}{Xiangguo Sun et al.  2018 IEEE International Conference on Communications (ICC)}

\bibitem{yash}
\href{https://sentic.net/predicting-personality-with-psycholinguistic-and-language-model-features.pdf}{Yash Mahta et al. Bottom-Up and Top-Down: Predicting Personality with Psycholinguistic and Language Model Features. 2020 IEEE International Conference on Data Mining (ICDM)}

\bibitem{hans}
\href{https://journalofbigdata.springeropen.com/articles/10.1186/s40537-021-00459-1}{Hans Christian et al. Text based personality prediction from multiple social media data sources using pre-trained language model and model averaging. Journal of Big Data volume 8, Article number: 68 (2021).}

\bibitem{yash_2}
\href{https://sentic.net/personality-detection-using-bagged-svm-over-bert.pdf}{Amirmohammad et al. Personality Trait Detection
Using Bagged SVM over BERT Word Embedding Ensembles.}

%% literature survey non-engineering (big5-MBTI)
\bibitem{big5}
\href{https://www.verywellmind.com/the-big-five-personality-dimensions-2795422}{The Big Five Personality Traits Explained}

\bibitem{MBTI}
\href{https://www.truity.com/myers-briggs/about-myers-briggs-personality-typing}{Myers-Briggs Type Personality Model Explained}



\bibitem{rest}
\href{https://www.ics.uci.edu/~fielding/pubs/dissertation/rest_arch_style.htm}{Roy Fielding. Fielding Dissertation: chapter 5. Representational State Transfer (REST).}

\bibitem{haar}
\href{https://ieeexplore.ieee.org/abstract/document/990517}{P. Viola; M. Jones. Rapid object detection using a boosted cascade of simple features. Proceedings of the 2001 IEEE Computer Society Conference on Computer Vision and Pattern Recognition. CVPR 2001}

\bibitem{xception}
\href{https://arxiv.org/abs/1610.02357}{Franc¸ois Chollet. Xception: Deep learning with depthwise separable convolutions. CoRR, abs/1610.02357, 2016}

\bibitem{He}
\href{https://arxiv.org/pdf/1512.03385.pdf}{Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun. Deep residual learning for image recognition. In Proceedings of the IEEE conference on computer vision and pattern recognition, pages 770–778, 2016.}

\bibitem{andrew}
\href{https://arxiv.org/abs/1704.04861}{Andrew G. Howard et al. Mobilenets: Efficient convolutional neural networks for mobile vision applications. CoRR, abs/1704.04861, 2017.}


% face challenges
\bibitem{facebook_takedown_dataset}
\href{https://sites.google.com/michalkosinski.com/mypersonality}{Facebook data set for personality analysis source.}
 
\bibitem{state_of_the_art_pers_text}
\href{https://paperswithcode.com/paper/recent-trends-in-deep-learning-based/review/?fbclid=IwAR2d33VKI_TmHxP06abC7OzJZYYZ3ahbqdw5kswAxHVC71kJKjhECMvdavk}{Recent Trends in Deep Learning Based Personality Detection.}

\bibitem{yash_personal}
\href{https://www.researchgate.net/profile/Yash-Mehta-16}{Yash Mehta. University College London | UCL · Gatsby Computational Neuroscience Unit. Research gate profile.}

\end{thebibliography}